Equalizer Programming Guide

### 2007-11-23 Developer/ProgrammingGuide/paper.tex
Update Programming Guide
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.1 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya and Jonas B\"osch.

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The \textsf{eqHello} redraw function renders six rotating, colored quads
around the origin. The \textsf{frameDraw} meth\-od provided by the
\textsf{eq::Channel} can be used as a convience function to setup the
frustum and other OpenGL state. After setting up some additional
lighting parameter, \textsf{eqHello} rotates the scene and render the
quads using immediate mode:

@@

Finally it is time to initialize the configuration. For statistics, the
time for this operation is measured and printed. During initialization
the server launches and connects all render client nodes, and calls the
appropriate initialization task methods, as explained in later
sections. \textsf{Config::init} does return after all nodes, pipes,
windows and channels are initialized. It returns \textsf{true} only if
all initialization task methods were successful.

@@

When the configuration was successfully initialized, the main rendering
loop is executed. The main loop runs until the user exits the
configuration, or when a maximum number of frames has been rendered,
when specified by a command-line argument. The latter is useful for
benchmarks. The \textsf{Clock} is reused for measuring the overall
performance. A new frame is started using \textsf{Config::startFrame}
and a frame is finished using \textsf{Config::finishFrame}.

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.2 for Equalizer 0.4+svn\\[\medskipamount]
  \today
}

@@

Written by Stefan Eilemann.\\
Engineering contributions by Maxim Makhinya, Jonas B\"osch and Christian Marten.

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

The \textsf{eqHello} redraw function renders six colored quads, rotating
around the origin. The \textsf{frameDraw} meth\-od provided by the
\textsf{eq::Channel} can be used as a convience function to setup the
frustum and other OpenGL state. After setting up some additional
lighting parameter, \textsf{eqHello} rotates the scene and renders the
quads using immediate mode:

@@

Finally it is time to initialize the configuration. For statistics, the
time for this operation is measured and printed. During initialization
the server launches and connects all render client nodes, and calls the
appropriate initialization task methods, as explained in later
sections. \textsf{Config::init} returns after all nodes, pipes,
windows and channels are initialized. It returns \textsf{true} only if
all initialization task methods were successful.

@@

When the configuration was successfully initialized, the main rendering
loop is executed. It runs until the user exits the
configuration, or when a maximum number of frames has been rendered,
specified by a command-line argument. The latter is useful for
benchmarks. The \textsf{Clock} is reused for measuring the overall
performance. A new frame is started using \textsf{Config::startFrame}
and a frame is finished using \textsf{Config::finishFrame}.
